A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-03 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
adding agent table

@@

\subsection{What are the effects of node failures on system behavior?}
Nodes may go offline or fail entireley. Since their participation in groups is critical to the 
success of the threshold relay, it is important to understand the impact of various levels
of failure on group characteristics. In particular, failures can result in disproportionate ownership
of groups which may cause a byzantine fault to occur.

\subsection{What are the effects of stake distributions on system behavior?}
Stake distributions can also skew ownership of groups and can lead to a byzantine fault. A more
centralized distribution could once again lead to a greater ownership of groups by a few entities
thus creating conditions for the group to be compromised.

@@

ADD table for Agent types

@@

\section{Results}
\subsection{Emergence of steady state behavior}
Using the single run experiment, we discover that system stabalizes to steady state
usually around 400 blocks, usually due to normalization of bootstrapping states. 
However, final steady state values for the percentage of total groups that are compromised
appears to vary significantly and is dependent on the degree of concentration in the 
stake distribution.

For concentrated distributions such as Ethereum, the steady state level of compromised
groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
distribution, we see steady steat levels within the 50-80 percent band for the given set
of parameters (NOTE PARAMETER SETTINGS) \ref{fig:steady_state}. We expect a similar band but at
different parameter levels for different parameter settings.

@@

\textit{Percent Compromised Groups} Steady state level of percent compromised
groups appears to

\subsection{Effects of Node failures on group and signature characteristics}

\begin{itemize}
    \item Effects of stake distributions on group and signature characteristics
    \item Additional analyses?
\end{itemize}

@@

\begin{figure*}[h]
    \onecolumn
    \centering
    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
    \multicolumn
\end{figure*}

>>>>

Agent based systems could help evaluate trends in behavior related to
various system parameters. They may not however, accurateley represent 
actual system performance.

Discuss levels of complexity, with citations. Why greater complexity may
not get you much more insight.

@@

\subsection{How could node failures affect system behavior?}
Nodes may go offline or fail entireley. Since their participation in groups is critical to the 
success of the threshold relay, it is important to understand the impact of various levels
of failure on group characteristics. In particular, failures can result in disproportionate ownership
of groups which may cause a byzantine fault to occur.

\subsection{How could different stake distributions affect system behavior?}
Stake distributions can also skew ownership of groups and can lead to a byzantine fault. A more
centralized distribution could once again lead to a greater ownership of groups by a few entities
thus creating conditions for the group to be compromised.

@@

ADD table for Agent types
\begin{table}[htbp]
    \caption{Agent Types}
    \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
    \textbf{Parameters}&\multicolumn{3}{|c|}{\textbf{Agents}} \\
    \cline{2-4} 
    \textbf{ } & \textbf{\textit{Node}}& \textbf{\textit{Group}}& \textbf{\textit{Signature}} \\
    \hline
    Unique ID & X & X & X \\
    \hline
    \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
    \end{tabular}
    \label{table}
    \end{center}
    \end{table}

Decide whether all parameters should be listed?

@@

\section{Results}
\subsection{Emergence of steady state behavior}
Using the single run experiment, we discover that system consistently appears to 
stabalizes to steady state usually around 400 blocks, and usually due to normalization of bootstrapping states. 
However, final steady state values for the percentage of total groups that are compromised
appears to vary significantly and is dependent on the degree of concentration in the 
stake distribution.

@@

\textit{Percent Compromised Groups} For concentrated distributions such as Ethereum, the steady state level of compromised
groups appears to vary between 0-100 percent (SHOW), with a tendancy to be either close
to 0 or close to 100. For distributions with greater spread, such as our hypothetical linear
distribution, we see steady steat levels within the 50-80 percent band for the given set
of parameters (NOTE PARAMETER SETTINGS) \ref{fig:steady_state}. We expect a similar band but at
different parameter levels for different parameter settings. (CHECK THIS AGAIN)

\textit{Percent Lynchpinned Signatures}

\subsection{Effects of Node failures on group and signature characteristics}
To evaluate the possible effects of node failure on group and signature characteristics, we use the
multi-run study. We then observe trends in the specific parameters discussed below.

\subsection{Effects of stake distributions on group and signature characteristics}

@@

\begin{figure*}[h]
    \onecolumn
    \centering
    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
\end{figure*}
